Sparsity Weak Lensing $3$-D Density Map Reconstruction: Reducing the line-of-sight smearing.

### 2020-10-25 doc/paper_ms_method_HSCY1/ms.tex
update to high resolution figures with mayavi

\begin{abstract}
A new method is developed to reconstruct $3$-D density contrast maps from photometric weak lensing shear measurements.
The $3$-D density contrast maps is modeled as a summation of NFW basis atoms which have $2$-D multi-scale NFW surface 
density profiles on the transverse plane and $1$-D Dirac delta functions in the line-of-sight direction. With the prior 
assumption that the density fields can be sparsely represented by the NFW basis atoms, it is reconstructed using an 
oracle algorithm: adaptive lasso. Our method is tested with realistic simulations using the HSC-like shape noise and 
photo-$z$ uncertainty.
{\redColor{Add descriptions on the outcomes of the test on the simulations.}}
\end{abstract}

@@

\begin{figure*}[!t]
\centering
\includegraphics[width=0.42\textwidth]{delta-3-7-pz-nn-lasso.png}
\includegraphics[width=0.42\textwidth]{delta-3-7-pz-nn-alasso.png}
\caption{The result of density map reconstruction with standard lasso (left) and adaptive lasso (right). The input density 
        map is from a NFW halo with mass $M_{200}=10^{15} ~h^{-1}M_{\odot}$ at redshift $0.35$. The lasso reconstruction 
        smear the density field along the line-of-sight direction. Noises on shear measurements are neglected in the 
        simulation.} \label{fig-lassoVsadaLasso}
\end{figure*}

@@

\begin{figure*}[!t]
\centering
\includegraphics[width=0.42\textwidth]{delta-1-7-pz-wn-PM-falsepeakproblem.png}
\includegraphics[width=0.42\textwidth]{delta-1-7-pz-wn-NFW-falsepeakproblem.png}
\caption{The result of density map reconstruction with  Point Mass atoms (left) and  NFW atoms (right). The input density 
        map is from a NFW halo with mass $M_{200}=10^{15.02} ~h^{-1}M_{\odot}$ at redshift $0.164$. The reconstruction 
        with point mass atoms has many false peaks at different redshfits.
        } \label{fig-lassoVsadaLasso}
\end{figure*}

>>>>

\begin{abstract}
A new method is developed to reconstruct $3$-D density contrast maps from photometric weak lensing shear measurements.
The $3$-D density contrast maps are modeled as a summation of the NFW basis atoms which have $2$-D multi-scale NFW surface 
density profiles on the transverse plane and $1$-D Dirac delta functions in the line-of-sight direction. With the prior 
assumption that the density fields can be sparsely represented by the NFW basis atoms, it is reconstructed using an 
oracle algorithm: adaptive lasso. Our method is tested with realistic simulations using the HSC-like shape noise and 
photo-$z$ uncertainty.
Our findings are summarized as folllows: 1) The global minima solution of the standard lasso algorithm suffers from a
smear of structure in the line-of-sight direction even in the absence of shape nosie.
2) The global minima solution of addaptive lasso algorithm significantly removes the line-of-sight smear of structure.
\end{abstract}

@@

\begin{figure*}[!t]
\centering
\includegraphics[width=0.49\textwidth]{delta-3-7-pz-nn-lasso.pdf}
\includegraphics[width=0.49\textwidth]{delta-3-7-pz-nn-alasso.pdf}
\caption{The result of density map reconstruction with standard lasso (left) and adaptive lasso (right). The input density 
        map is from a NFW halo with mass $M_{200}=10^{15} ~h^{-1}M_{\odot}$ at redshift $0.35$. The lasso reconstruction 
        smear the density field along the line-of-sight direction. Noises on shear measurements are neglected in the 
        simulation.} \label{fig-lassoVsadaLasso}
\end{figure*}

@@

\begin{figure*}[!t]
\centering
\includegraphics[width=0.49\textwidth]{delta-1-7-pz-wn-PM-falsepeakproblem.pdf}
\includegraphics[width=0.49\textwidth]{delta-1-7-pz-wn-NFW-falsepeakproblem.pdf}
\caption{The result of density map reconstruction with  Point Mass atoms (left) and  NFW atoms (right). The input density 
        map is from a NFW halo with mass $M_{200}=10^{15.02} ~h^{-1}M_{\odot}$ at redshift $0.164$. The reconstruction 
        with point mass atoms has many false peaks at different redshfits.
        } \label{fig-lassoVsadaLasso}
\end{figure*}
